---
title: "Teaching Statistics and Data Science"
subtitle: "STAT 375 UC Berkeley"
logo: "../assets/images/stat-375-hex.png"
format: 
  revealjs:
    theme: "../assets/css/slides.scss"
    multiplex: true
    transition: fade
    slide-number: true
    incremental: true 
---

## Agenda

1.  Introductions

2.  Course Structure

3.  Community Standards

4.  Asking Why


## Meet your group

-   In your groups, take turns introducing yourselves and sharing:
    -   Your name and preferred pronouns
    -   Your year and major
    -   What class you are teaching
    -   Memory of your best teacher and what made them so effective
-   You have 7 minutes

```{r}
countdown::countdown(7, top = 0)
```

# Introductions

## Course Structure

Syllabus available on course website:

:::{style="text-align: center"}
<>
:::

## Community Standards

In your groups, please agree upon:

1.  Three adjectives that describe a class environment is **conducive** to everyone learning
2.  Three adjectives that describe a class environment that is **not conducive** to everyone learning

. . . 

Then post them to the padlet:

[<https://tinyurl.com/mrvpdpnp>]{style="font-size: 1.5em"}

You have 8 minutes.

```{r}
countdown::countdown(8, top = 0)
```

# Course Goals

> Train the habit of asking *why* you are teaching something one way or another.

> Judge your teaching not by your knowledge of statistics / data science, but by your student's.

# Critique of this class so far...

## 

What worked? What didn't? How can we change it?

::: columns
::: {.column width = "50%"} \### Meet your group - What was the goal? - How big should the groups be? - Which questions?

### Introductions

-   How personal should you be?
:::

::: {.column width = "50%"} \### Syllabus - What were your main takeaways? - How else could this information be presented?

### Community Standards

-   What was the feel of the group discussion?
-   Was everyone participating? :::

::::

# Break until 3:15

# GSI Panel

### Isaac Schmidt

### Chad Breece
